%!TEX root = ../hotmobile13-report.tex
\section{Posters \& Demos}
\label{sec:postersdemos}
%[first position]: Bringing In-situ Social Awareness to Mobile Systems: Conversational Turn Monitoring and its Applications
%Youngki Lee, Chulhong Min, Chanyou Hwang, Jaeung Lee, Inseok Hwang, Chungkuk Yoo, Junehwa Song (Kaist, Korea)
Winner of the best poster\slash demo award, ``Bringing In-situ Social Awareness to Mobile 
Systems: Conversational Turn Monitoring and its
Applications''~\cite{lee13} (Lee et al., 
KAIST) attracted significant attention and discussion from attendees. Their 
system uses the smartphone as a mechanism for encouraging in-person interactions
by monitoring conversation patterns. The demo was supported by a video of the 
system in use in a nursery -- encouraging peer-engagement from an otherwise 
withdrawn autistic child. By combining the video with a layout of smartphones 
running their turn-monitoring system (which used coloured bars to indicate 
speakers and conversation duration), attendees were able to see a clear 
demonstration of the capability of the system as well as potential applications
and were rewarded for their interactions with the demonstrators with a clear
representation of their conversation patterns.

%[second position]: Mitigating Distractions from Smartphones
%Connor Bain, Sanorita Dey, Srihari Nelakuditi (University of South Carolina), Romit Roy Choudhury (Duke University)
``Leveraging Imperfections of Sensor for Fingerprinting
Smartphones''~\cite{dey13}
(Dey et al., University of South Carolina) received an honourable mention
as the second best poster\slash demo of ACM HotMobile'13. Their work suggests
uniquely identifying smartphones by comparing the responses from a given
stimulus applied to a built-in sensor chip of different devices. As
imperfections from manufacturing these chips can subtlety affect their
reading responses, sensor fingerprinting seems to be a promising
alternative for telling devices apart, especially considering that
smartphone IMEI codes can be duplicated.

%[third position] Focus: A Usable & Effective Approach to OLED Display Power Management
%Tan Kiat Wee, Tadashi Okoshi, Archan Misra, Rajesh Krishna Balan (Singapore Management University)
Wee at al.'s demo (Singapore Management University), ``Focus: A Usable \&
Effective Approach to OLED Display Power Management''~\cite{wee13}
received the award
for third best poster\slash demo. Following on from some of the power
management discussions, this demo showed how power saving can be achieved
by powering off sections of the screen that do not need to be displayed.
Conference attendees could create their own dimming profile for one of a
number of predefined Android applications. Their demo allowed attendees to
explore the usability of an application with dimmed portions (most often
the unused lower portions of the screen) and to see the potential
battery-life gains.
